Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-10-18 crowdsource/article.tex
small modifs

A partial correlation approach \cite{sutera2014simple}  is a simple yet
effective solution to the problem of connectome inference in calcium imaging
data. This partial correlation statistics, the inverse of the correlation
measure, has  the property to filter indirect associations between neurons and
gives a high degree of association between directly connected neurons. The
winning solution of the Connectomics challenge combines two main steps:
(i) data are pre-processed using signal processing filters; (ii)
the network is infered through partial correlation. The pre-processing step
highly improves the infered network by removing noise and taking into account
specifities of the fluorecense signals.

>>>>

A partial correlation approach \cite{sutera2014simple}  is a simple yet
effective solution to the problem of connectome inference from calcium imaging
data. This partial correlation statistics, equivalent to the inverse of the correlation
measure, has  the property to filter out indirect associations between neurons and
only gives a high degree of association between directly connected neurons. The
winning solution of the Connectomics challenge combines two main steps:
(i) A pre-processing of the data using signal processing filters; and (ii)
The inference of the network through partial correlation. The pre-processing procedure
highly improves the infered network quality by filtering out noise and taking into account
specifities of the fluorecense signals.
